Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-19 paper/paper.tex
Add results explanation

@@

Line charts with benchmarks of mentioned algorithms on different noise images
are shown on \Cref{fig:overall}.

@@

@@

\begin{figure}
  \centering
  \inputnorm{DFS}{DFS optimizations}
  \inputnorm{SUF}{SUF optimizations}
  \inputnorm{SUF2}{SUF2 optimizations}
  \inputnorm{DTSUF}{SUF optimizations, relative to DTSUF performance}
  \caption{Speedup/density charts}
  \label{fig:normed}
\end{figure}

>>>>

Benchmarks showed that for random images, the run time depends non-trivially on
the value of density $d$, which is the ratio of object pixels in the image. On
the one hand, this is because all of the considered algorithms pass background
pixels without any processing, and somehow process the object pixels, so the
exact number of operations such as Union and Find should generally grow with
$d$. On the other hand, the greater the value of $d$, the less number of CC is
likely to be present in the image, which reduces the number of relatively
expensive Union operations.

So benchmarks were run for several values of $d$ to achieve a picture of how the
speedup depends on the number of object pixels in the image.

@@

The overall benchmark line plot of all algorithms and optimizations is
presented on \Cref{fig:overall}.

@@

To show more closely how efficient the optimizations actually appear to be, we
plotted speedup/density charts for the considered methods (\Cref{fig:normed}).
Here the speedup of algorithm A relative to algorithm B is defined as
$\frac{T_B}{T_A}$, where $T_A$ and $T_B$ are the total times used by the
corresponding algorithms to count CC in all the test images of same density.
The greater the speedup of optimized method relative to original method, the
more efficient the optimization is considered.

@@

\begin{figure}
  \centering
  \inputnorm{DFS}{DFS optimizations}
  \inputnorm{SUF}{SUF optimizations}
  \inputnorm{SUF2}{SUF2 optimizations}
  \inputnorm{DTSUF}{SUF optimizations, relative to DTSUF}
  \caption{Speedup/density charts}
  \label{fig:normed}
\end{figure}

The speedup plots on \Cref{fig:normed:DFS,fig:normed:SUF,fig:normed:SUF2}
suggest that the ``2x2 copy'' optimization speeds up the considered methods by
factor greater than 1 for all tested densities. On the other hand, the
``2x2 view'' optimization is showed to be not time-efficient at all for some
densities, slowing down DFS and SUF2 if run on images with densities less than
38\% and 28\% respectively. Utilizing the latter optimization also does not
speed up SUF on images on density approaching 20\%, although it does not slow
down the algorithms either.

The worst-case and best-case speedups are shown on the \autoref{tab:speedup}.
Here we see that while ``2x2 view'' optimization is more memory-efficient than
``2x2 copy'', it can slow down the method in some situations, and generally it
does not give as much performance advantage.

We should also mention the chart on \autoref{fig:normed:DTSUF}, featuring
speedup of our SUF optimizations relative to DTSUF in order to compare our
optimizations to the optimization by Wu, Otoo and Suzuki. The plot clearly shows
that for all the densities under 80\% our ``SUF on 2x2 copy'' algorithm
outperforms the decision-tree based approach by the factor of at least
$1.5$, with speedup reaching $2.5$ for 2\% density.

\begin{table}
  \centering
  \begin{tabular}{l|c|c|c|c}
    Algorithm & worst speedup & worst speedup density & best speedup & best
    speedup density \\
    \hline
    \input{tables/speedup}
  \end{tabular}
  \caption{The worst and the worst speedups of the considered optimizations}
  \label{tab:speedup}
\end{table}
